
%----------------------------------------------------------------------------------------
%	Programming Journey
%----------------------------------------------------------------------------------------

\cvsect{Programming Journey}

\begin{entrylist}
	\entry
		{Primary School}
		{Lua with ComputerCraft}
		{Personal}
		{\\
			My initiation into the world of programming began in 2012, thanks to Minecraft. I delved into modded Minecraft and stumbled upon ComputerCraft, a mod that ingeniously incorporated DOS-like computers within the game. Fascinatingly, these virtual computers were programmable using Lua, enabling me to tinker with existing programs and eventually create and execute my first programs.

			\vspace{0.5cm}
			\Label{black}{Lua}
		}
	\entry
		{Secondary School}
		{Exploring core programming concepts through different languages}
		{Personal and Education}
		{\\
			Early in my secondary school days, I was introduced to a few graphical programming languages. These primarily consisted of drag-and-drop interfaces designed for script construction. However, the real intrigue came a couple of years later, when I encountered Visual Basic. Here, I embarked on creating console-based conversational trees, deepening my understanding of logical flows and interactivity.

			\vspace{0.5cm}

			My enthusiasm for Minecraft did not wane; in fact, it spurred a personal challenge. Determined to put my own spin on the game, I delved into Java, teaching myself through a plethora of online tutorials. My perseverance bore fruit as I successfully managed to both create new Minecraft mods and recreate existing ones, allowing me to tailor my gameplay experience and furthering my programming prowess.

			\vspace{0.5cm}

			My GCSE years in secondary school marked another milestone in my programming journey. I was introduced to Python 2.7 in my computer science class, which further refined my programming skills and expanded my knowledge of software development principles.

			\vspace{0.5cm}


			\Label{black}{Java} \Label{black}{Visual Basic} \Label{black}{Python 2.7}
		}
	\entry
		{College}
		{C\# and Beyond in Apprenticeship}
		{Education}
		{\\
			Upon completing secondary school, I wasted no time and immediately began my first apprenticeship.

			As I transitioned into my apprenticeship, my programming journey took a more nuanced turn. I not only learned C\# but also harnessed its synergy with SQL to develop MVC applications. It was during this period that I was formally introduced to Object-Oriented Programming (OOP). A later module also covered foundational web technologies and I had to develop an interactive web-app from the ground up in HTML, CSS, and JS.

			My understanding deepened as I familiarised myself with core principles including Pareto, DRY, SOLID, YAGNI, the Law of Demeter (LoD), Conway's Law, and the concepts of Cohesion and Coupling.

			\vspace{0.5cm}
			\Label{black}{C\#} \Label{black}{SQL} \Label{black}{HTML} \Label{black}{CSS} \Label{black}{JS}
		}
	\entry
		{Labman}
		{First job in Software : IT and IPC Control Systems}
		{Work}
		{\\
			My tenure at Labman, which was an integral part of my college apprenticeship, presented a unique set of challenges and opportunities. Initially, given the time-intensive nature of my mentor's high-value project, my exposure to the intricacies of software engineering was limited. As such, much of my role was characterised by generic IT tasks, encompassing a wide spectrum of responsibilities. \\

		However, as my time at Labman drew closer to its conclusion, I found myself integrated into a dynamic team. In these final two months, I collaborated closely with an electrical engineer and a senior software engineer, working on a pivotal project. Here, I ventured into programming for Beckhoff IPCs, working in both Ladder Logic and Structured Text. Furthermore, I honed my skills in SQL and contributed alongside my team, who were engaged in crafting a core component in C++.

			\vspace{0.5cm}
			\Label{black}{C\#} \Label{black}{SQL} \Label{black}{Structured Text} \Label{black}{Ladder Logic}
		}
	\entry
		{AdmitMe}
		{Second Job in Software: Web Development}
		{Work}
		{\\
			Transitioning from Labman, my college presented a new opportunity for me at a budding local start-up named 'Admit Me'. As I embarked on my journey as a web developer, I quickly grasped the volatility of the role — finding myself as essentially the sole employee in this venture. Despite the inherent challenges and brevity of my tenure, it was a period of rapid enlightenment. It was here that I delved into the vast expanse of web development, encountering tools and frameworks like Ruby On Rails, Bootstrap, and PostgreSQL. I rapidly assimilated these technologies, constructing web scrapers and delivering websites for clients under tight deadlines. While the role was transient, the exposure and experience I gained were invaluable.

			\vspace{0.5cm}

			\Label{black}{Ruby On Rails} \Label{black}{HTML} \Label{black}{SCSS}
		}
	\entry
		{Tascomp}
		{<Insert Header>}
		{Work}
		{\\
			<Insert Description>

			\vspace{0.5cm}
			\Label{black}{C} \Label{black}{C++} \Label{black}{C++/CLI} \Label{black}{MFC} \Label{black}{.NET} \Label{black}{SLANG} \Label{black}{SQL Server} \Label{black}{Win32}
		}
	\entry
		{University}
		{Taking on an Up-skilling degree}
		{Education}
		{\\
			<Insert Description>

			\vspace{0.5cm}
			\Label{black}{Java} \Label{black}{Git} \Label{black}{Markdown} \Label{black}{LaTeX}
		}
	\entry
		{Personal Projects}
		{<Insert Header>}
		{Personal}
		{\\
			<Insert Description>

			\vspace{0.5cm}
			\Label{black}{Lua} \Label{black}{Java} \Label{black}{Dart} \Label{black}{Flutter} \Label{black}{Rust} \Label{black}{SCAD} \Label{black}{C} \Label{black}{C++} \Label{black}{Bash} \Label{black}{Linux}
		}
\end{entrylist}

\vspace{1cm}	